---
title: "MixTox_Transcriptomics_Downstream_Analysis"
author: "Vaskar Mukherjee"
date: "9/9/2021"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# TRANSCRIPTOMIC ANALYSIS

In this project we used high‐throughput phenomics to identify synergistic or antagonistic interactions in chemical mixtures in the yeast Saccharomyces cerevisiae and Debaryomyces hansenii and used transcriptomic analysis to understand the mechanistic basis of the interactions.

Transcriptomics analysis to understand the mechanistic basis of chemical interactions was performed for two chemical interactions for growth rate (growth during the exponential growth phase), identified in our phenomics experiment, that were conserved in both species i.e. NaCl and rapamycin synergism, and salt and paraquat antagonism.

The details of the transcriptomic samples are given in **RAW_DATA_TRANSCRIPTOMICS/SAMPLE_DETAILS.xlsx**

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
